|

### 2024-08-09 doc/paper.qmd
update paper.qmd

The aim of the following paper is to illustrate how to use open science tools in empirical accounting research. The original study by @Leuz_2003 examines systematic differences in earnings management (EM) across 31 countries and proposes that these differences are influenced by the level of investor protection. Specifically, they argue that stronger investor protection reduces earnings management by limiting insiders’ ability to acquire private control benefits.

@@

The analysis includes pulling and filtering the relevant financial data, identifying relevant companies and countries based on the authors’ requirements, calculating the EM measures for each country, and examining the relationship between each country’s aggregate earnings management score and its ranking based on explicit assumptions made whenever the paper by @Leuz_2003 is not clear on how to proceed. The complete computation code for EM measures is available in `code/python/do_analysis.py` for detailed review if necessary. Code snippets will be presented only in exceptional cases to highlight specific points. @

The replicated table is shown below, followed by replication steps documentation, a detailed comparison, and discussion of the results.

@@

# Results
##Cross-check your results with the original table to ensure accuracy. Compare your results with the results in the paper. If you notice differences, discuss where they may originate. Make sure to be as specific as possible. This could involve looking at the data selection, calculation methods, or any assumptions that might differ from the original; changes in the data over time, different interpretations of the methodology, or limitations in the data sources used. Consider whether the differences are significant and what they might mean for the conclusions drawn in the paper.

@@

# Conclusion

>>>>

The aim of the following paper is to illustrate how to use open science tools in empirical accounting research.

The original study by @Leuz_2003 examines systematic differences in earnings management (EM) across 31 countries and proposes that these differences are influenced by the level of investor protection. Specifically, they argue that stronger investor protection reduces earnings management by limiting insiders’ ability to acquire private control benefits.

@@

The analysis includes pulling and filtering the relevant financial data, identifying relevant companies and countries based on the authors’ requirements, calculating the EM measures for each country, and examining the relationship between each country’s aggregate earnings management score and its ranking based on explicit assumptions made whenever the paper by @Leuz_2003 is not clear on how to proceed. The complete computation code for EM measures is available in `code/python/do_analysis.py` for detailed review if necessary. Code snippets will be presented only in exceptional cases to highlight specific points.

The replicated table is shown below, followed by the research design assumptions in @sec-research_design_assumptions, documentation of the replication steps in @sec-replication_steps, a detailed comparison in @sec-results, and concluding remarks in @sec-conclusion.

@@

# Results {#sec-results}
##Cross-check your results with the original table to ensure accuracy. Compare your results with the results in the paper. If you notice differences, discuss where they may originate. Make sure to be as specific as possible. This could involve looking at the data selection, calculation methods, or any assumptions that might differ from the original; changes in the data over time, different interpretations of the methodology, or limitations in the data sources used. Consider whether the differences are significant and what they might mean for the conclusions drawn in the paper.

@@

# Conclusion {#sec-conclusion}
